Z-Resonance at LEP

### 2010-08-04 Z0-Publikation/tex/paper-template.tex
kleine sachen, vllt neue hadr. breite

\setlength{\marginparwidth}{1cm}
\usepackage[textsize=tiny,colorinlistoftodos%,disable
]{todonotes}
\begin{document}
\hugehead

@@

\title{Z-Resonance at LEP}
\titlerunning{Z-Resonance at LEP}
\authorrunning{Thomas Murach, Robert Riemann}
\author{{\bf Draft Version 1.1}\\
\medskip \\
Thomas Murach,$^{1}$
Robert Riemann$^{1}$
} 
\institute{$^1$Department of Physics, Humboldt University of Berlin, Germany\\}  
\date{Received: \today / Revised version: 0.1}
\abstract{
This paper describes the analysis of the L3 detector data taken at different
center of mass energies around \SI{90}{\GeV}, which reveals the properties of
the $Z$-Boson. Additionally the weak mixing angle and the colour factor are determined.
The Z-boson mass is evaluated to $M_Z = \SI{91.16(3)}{\GeV}$ with a decay width
of $Γ_Z = \SI{2.61(6)}{\GeV}$.
The weak mixing angle is computed to $\sin² Θ_W = \num{0.23(9)}$ and the colour
factor to $N_C = \num{3.2(13)}$.
All resuls are in good agreement to the standard model and can be considered as
a confirmation of it.
}
\maketitle

@@

\subsection{Determination of the leptonic decay width}
Through the knowledge of the overall cross section it is possible to calculate
the leptonic decay width $Γ_l$. First of all we assume that the decay width is
the same for all leptons. We can use the following formula for determining it
by using the fit parameter for the muonic cross section:
\begin{equation}
σ_0^μ = \frac{12π}{M_Z^2}\frac{Γ_l^2}{Γ_Z^2}.
\label{eqn:leptonicwidth}
\end{equation}
This equation can easily be solved to determine the resulting leptonic decay
width $Γ_l$, because all the other variables are known.
\begin{equation}
Γ_l = (91 \pm 2 \pm 1)\si{\mega\electronvolt}
\label{eqn:leptonicwidthresult}
\end{equation}
In order to calculate the leptonic decay width, it is also possible to utilize
the following equation:
\begin{equation}
Γ_l = \frac{1}{3}(Γ_Z - 3Γ_{\mathrm{Had}} - 3Γ_{ν_l}).
\end{equation}
$Γ_{\mathrm{Had}}$ can be calculated in the same way as the leptonic decay
width in \eref{leptonicwidth}. $Γ_{ν_l}$ can be determinde by using the
following relation:
\begin{eqnarray}
Γ_{ν_e} &=& \frac{G_FM_Z^3}{12\sqrt{2}π}\\
&=& (165.71 \pm 0.10 \pm 0.09)\si{\mega\electronvolt}
\end{eqnarray}
Now the leptonic decay width $Γ_l$ can be evaluated.
\begin{equation}
Γ_l = (83 \pm 4 \pm 3) \si{\mega\electronvolt}
\end{equation}
This is in the same order of magnitude like the result shown in
\eref{leptonicwidthresult}.

@@

Finally the measurements allow also to calculate the colour factor $N_C$ using
$Γ_{\mathrm{had}}$. The hadronic decay width can be obtained by two formulas.
This width can be computed, as the overall $Γ_Z$ in known, but also the components
$Γ_{ν_e}$ and $Γ_l$.
\begin{equation}
 Γ_Z = Γ_{\mathrm{had}} + 3Γ_{ν_e} + 3Γ_l
 \label{eqn:gammahad1}
\end{equation}
In reference to the standard model there is a second way to compute $Γ_{\mathrm{had}}$.
\begin{equation}
 Γ_{\mathrm{had}} = N_C \cdot K_{QCD}\cdot ( 2Γ_u + 3Γ_d )
 \label{eqn:gammahad2}
\end{equation}
Replacing $Γ_{\mathrm{had}}$ in \eref{gammahad2} using \eref{gammahad1} leads to a
formula which allows to compute the colour factor $N_C$.
\begin{equation}
 N_C = 3.20 \pm 0.11 \pm 0.07
\end{equation}
This result confirms, that there are no new quarks to be expected with a mass
lower than around \SI{90}{\GeV}\todo{richtig?}.

>>>>

\setlength{\marginparwidth}{1cm}
\usepackage[textsize=tiny,colorinlistoftodos]{todonotes}
\begin{document}
\hugehead

@@

\title{Z-Resonance at LEP}
\titlerunning{Z-Resonance at LEP}
\authorrunning{Thomas Murach, Robert Riemann}
\author{{\bf Draft Version 1.1}\\
\medskip \\
Thomas Murach,$^{1}$
Robert Riemann$^{1}$
} 
\institute{$^1$Department of Physics, Humboldt University of Berlin, Germany\\}  
\date{Received: \today / Revised version: 0.1}
\abstract{
This paper describes the analysis of the L3 detector data taken at different
center of mass energies around \SI{90}{\GeV}, which reveals the properties of
the $Z$-Boson. Additionally the weak mixing angle and the colour factor are determined.
The Z-boson mass is evaluated to $M_Z = \SI{91.16(3)}{\GeV}$ with a decay width
of $Γ_Z = \SI{2.61(6)}{\GeV}$.
The weak mixing angle is computed to $\sin² Θ_W = \num{0.23(9)}$ and the colour
factor to $N_C = \num{3.2(13)}$.
All resuls are in good agreement to the standard model and can be considered as
a confirmation of it.
}

\maketitle

@@

\subsection{Determination of the leptonic decay width}
Through the knowledge of the overall cross section it is possible to calculate
the leptonic decay width $Γ_l$. First of all we assume that the decay width is
the same for all leptons. We can use the following formula for determining it
by using the fit parameter for the muonic cross section:
\begin{equation}
σ_0^μ = \frac{12π}{M_Z^2}\frac{Γ_l^2}{Γ_Z^2}.
\label{eqn:leptonicwidth}
\end{equation}
This equation can easily be solved to determine the resulting leptonic decay
width $Γ_l$, because all the other variables are known.
\begin{equation}
Γ_l = (91 \pm 2 \pm 1)\si{\mega\electronvolt}
\label{eqn:leptonicwidthresult}
\end{equation}
In order to calculate the leptonic decay width, it is also possible to utilize
the following equation:
\begin{equation}
Γ_l = \frac{1}{3}(Γ_Z - 3Γ_{\mathrm{Had}} - 3Γ_{ν_l}).
\end{equation}
$Γ_{\mathrm{Had}}$ can be calculated in the same way as the leptonic decay
width in \eref{leptonicwidth}. $Γ_{ν_l}$ can be determinde by using the
following relation:
\begin{eqnarray}
Γ_{ν_e} &=& \frac{G_FM_Z^3}{12\sqrt{2}π}\\
&=& (165.71 \pm 0.10 \pm 0.09)\si{\mega\electronvolt}
\end{eqnarray}
Now the leptonic decay width $Γ_l$ can be evaluated.
\begin{equation}
Γ_l = (83 \pm 4 \pm 3) \si{\mega\electronvolt}
\end{equation}
This is in the same order of magnitude as the result shown in
\eref{leptonicwidthresult}.

@@

Finally the measurements allow also to calculate the colour factor $N_C$ using
$Γ_{\mathrm{had}}$. The hadronic decay width can be obtained by two formulas.
This width can be computed, as the overall $Γ_Z$ in known, but also the components
$Γ_{ν_e}$ and $Γ_l$.
\begin{equation}
 Γ_Z = Γ_{\mathrm{had}} + 3Γ_{ν_e} + 3Γ_l
 \label{eqn:gammahad1}
\end{equation}
In reference to the standard model there is a second way to compute $Γ_{\mathrm{had}}$.
\begin{equation}
 Γ_{\mathrm{had}} = N_C \cdot K_{QCD}\cdot ( 2Γ_u + 3Γ_d )
 \label{eqn:gammahad2}
\end{equation}
Replacing $Γ_{\mathrm{had}}$ in \eref{gammahad2} using \eref{gammahad1} leads to a
formula which allows to compute the colour factor $N_C$.
\begin{equation}
 N_C = 3.20 \pm 0.11 \pm 0.07
\end{equation}
This result confirms, that there are no new quarks to be expected with a mass
lower than some \SI{90}{\GeV}.
